Assignment 1: Data and Descriptive

### 2023-11-01 MSB104_GR_1_Final_Assignment_research_article.qmd
code

---
title: "Regional Inequalities and economic growth; cross section and times series analysis"
author: "Anine Therese Karlsen & Mona Lisa Jones"
format: pdf
abstract: "This assignment aims to acquire, process, and analyze sub-national GDP and population data for a subset of European countries. Calculate GDP per capita and explore regional inequity using various descriptive statistics and visualizations.Furthermore examining the relationship between regional development and inequality, employing cross sectional estimation techniques for the year 2010."
editor: visual
bibliography: [Econometrics.bib]
output-file: Assignment1.qmd
page-layout: full
number-sections: true
papersize: a4
---

>>>>

---
title: "Regional Inequalities and economic growth; cross section and times series analysis"
author: "Anine Therese Karlsen & Mona Lisa Jones"
format: pdf
abstract: "This assignment aims to acquire, process, and analyze sub-national GDP and population data for a subset of European countries. Calculate GDP per capita and explore regional inequity using various descriptive statistics and visualizations.Furthermore examining the relationship between regional development and inequality, employing cross sectional estimation techniques for the year 2010."
editor: visual
bibliography: [Regional_inequality_23.bib]
output-file: Assignment1.qmd
page-layout: full
number-sections: true
papersize: a4
---

### 2023-11-01 assignment_1.qmd
code

@@

# References

>>>>

...

@@

What does the GINI really tell us? (Look at paper from page 116)

# Assignment 2: Cross-sectional Estimates

## 2A: Growth and Inequity

### 1. Model Estimation

```{r}
data2010_nuts2 <- gini_nuts_2 %>%
 group_by(id_nuts2, year) %>%
 mutate( gdp_n2 = sum(GDP, na.rm = T),
 pop_n2 = sum(population, na.rm = T),
GDP_per_capita = gdp_n2/pop_n2) %>%
 ungroup() %>%
 distinct(year, id_nuts0, id_nuts2, GDP_per_capita, gini_n2, gdp_n2, pop_n2) %>% 
  filter(year == 2010, gini_n2 > 0)

data2010_nuts2 <- data2010_nuts2 %>% 
  mutate(log_GDP_pc = log(GDP_per_capita))
```
